Analysing number of case and control based on new harmonised definition

### 2017-04-15 code/Rmd/harmonisedCaseControl.Rmd
Minor sanity fix

```{r new.dx}
all.mtd$ROSMAP$nDx = 'OTHER'
all.mtd$ROSMAP$nDx[all.mtd$ROSMAP$cogdx==1 & all.mtd$ROSMAP$braaksc <= 3 & all.mtd$ROSMAP$ceradsc <= 1] = 'CONTROL'
all.mtd$ROSMAP$nDx[all.mtd$ROSMAP$cogdx==4 & all.mtd$ROSMAP$braaksc >= 4 & all.mtd$ROSMAP$ceradsc >= 2] = 'AD'

>>>>

```{r new.dx}
all.mtd$ROSMAP$nDx = 'OTHER'
all.mtd$ROSMAP$nDx[all.mtd$ROSMAP$cogdx==1 & all.mtd$ROSMAP$braaksc <= 3 & all.mtd$ROSMAP$ceradsc >= 3] = 'CONTROL'
all.mtd$ROSMAP$nDx[all.mtd$ROSMAP$cogdx==4 & all.mtd$ROSMAP$braaksc >= 4 & all.mtd$ROSMAP$ceradsc <= 2] = 'AD'
